%%
%% Package includes to provide the basic style
%%
%\usepackage{harvard}    % Uses harvard style referencing
\usepackage{graphicx}   % Permits import of various graphics formats
\usepackage{hyperref}   % Provides hyperlinks to sections automatically
\usepackage{pdflscape}  % Provides landscape mode for end code listings
\usepackage{multicol}   % Provides ability to split output into columns
\usepackage{listings}   % Provides styled code listings

%%
%% Set some page size changes from the standard article class
%%
\usepackage[inner=4cm]{geometry}
%\usepackage{calc}
%\setlength{\parskip}{6pt}
%\setlength{\parindent}{0pt}
%\addtolength{\hoffset}{-0.5cm}
%\addtolength{\textwidth}{2.5cm}

%%
%% Format definitions for the style
%%





%\bibliographystyle{agsm}  %{alpha}
%\citationstyle{dcu}
\pagestyle{headings}
\fussy


%%
%% Definitions to provide layout in the dissertation title pages
%%
\newenvironment{spaced}[1]
  {\begin{minipage}[c]{\textwidth}\vspace{#1}}
  {\end{minipage}}


\newenvironment{centrespaced}[2]
  {\begin{center}\begin{minipage}[c]{#1}\vspace{#2}}
  {\end{minipage}\end{center}}


\newcommand{\declaration}[2]{
  \thispagestyle{empty}
  \begin{spaced}{4em}
    \begin{center}
      \LARGE\textbf{#1}
    \end{center}
  \end{spaced}
  \begin{spaced}{3em}
    \begin{center}
      Submitted by: #2
    \end{center}
  \end{spaced}
  \begin{spaced}{5em}
    \section*{COPYRIGHT}

    Attention is drawn to the fact that copyright of this dissertation rests
    with its author. The Intellectual Property Rights of the products
    produced as part of the project belong to the author unless otherwise specified
    below, in accordance with the University of Bath's policy on intellectual property 
   (see http://www.bath.ac.uk/ordinances/22.pdf).

    This copy of the dissertation has been supplied on condition that anyone
    who consults it is understood to recognise that its copyright rests with its
    author and that no quotation from the dissertation and no information
    derived from it may be published without the prior written consent of
    the author.

    \section*{Declaration}
    This dissertation is submitted to the University of Bath in accordance
    with the requirements of the degree of Bachelor of Science in the
    Department of Computer Science. No portion of the work in this dissertation
    has been submitted in support of an application for any other degree
    or qualification of this or any other university or institution of learning.
    Except where specifically acknowledged, it is the work of the author.
  \end{spaced}

  \begin{spaced}{5em}
    Signed:
  \end{spaced}
  }


\newcommand{\consultation}[1]{%
\thispagestyle{empty}
\begin{centrespaced}{0.8\textwidth}{0.4\textheight}
\ifnum #1 = 0
This dissertation may be made available for consultation within the
University Library and may be photocopied or lent to other libraries
for the purposes of consultation.
\else
This dissertation may not be consulted, photocopied or lent to other
libraries without the permission of the author for #1 
\ifnum #1 = 1
year
\else
years
\fi
from the date of submission of the dissertation.
\fi
\vspace{4em}

Signed:
\end{centrespaced}
}

%%
%% END OF DEFINITIONS
%%

% TODO notes
\usepackage[dvipsnames]{xcolor}

% for tables
\usepackage{booktabs}
%\usepackage[table,xcdraw]{xcolor}

% for references
\usepackage[noabbrev,capitalise,nameinlink]{cleveref}

\usepackage{subcaption} % used for multiple figures on same line
\usepackage{graphicx}
\graphicspath{ {./images/litreview/} }
\newcommand*{\doi}[1]{\href{https://doi.org/\detokenize{#1}}{doi: \detokenize{#1}}}

\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}

% for degrees symbol \degree
\usepackage{textcomp}
\usepackage{gensymb}

% for drawing arrows
\usepackage{tikz-cd}
\usepackage{tikz}
\usetikzlibrary{mindmap}


\usepackage{natbib}
\bibliographystyle{unsrtnat}
\setcitestyle{authoryear,open={(},close={)}}
\newcommand{\possessivecite}[1]{\citeauthor{#1}{\textcolor{blue}{'s}} (\citeyear{#1})}
\newcommand{\footurl}[2]{\href{#1}{#2}\footnote{\url{#1}}}


% Set this to the language you want to use in your code listings (if any)
\usepackage{bera}
\usepackage{times}

\lstset{
    breaklines,
    breakatwhitespace,
    basicstyle=\small,
    commentstyle=\color{OliveGreen},    % comment style
    escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
    keywordstyle=\color{blue},       % keyword style
    stringstyle=\color{Mulberry},
    emphstyle=\color{Maroon},
    numbers=left,
    frame=single,
    tabsize=2
}

\lstdefinestyle{python}{
    language=python,
    emph={cv},
}

\lstdefinestyle{cpp}{
    language=c++,
    emph={cv,aruco,ucoslam,spdlog}
}

\lstdefinestyle{java}{
    language=java
}

% patch first line numbers
\usepackage{etoolbox}% http://ctan.org/pkg/etoolbox
\makeatletter
\patchcmd{\lst@GLI@}% <command>
  {\def\lst@firstline{#1\relax}}% <search>
  {\def\lst@firstline{#1\relax}\def\lst@firstnumber{#1\relax}}% <replace>
  {\typeout{listings firstnumber=firstline}}% <success>
  {\typeout{listings firstnumber not set}}% <failure>
\makeatother

% Mini table of contents
\usepackage{minitoc}

% Larger column separation
\setlength{\columnsep}{35pt}

\usepackage{wrapfig}