\chapter{Ethics}\label{chap:ethics}

\subsubsection{Have you prepared a briefing script for volunteers?}
Yes, the participants have been briefed on the brainstorm study. They have been made aware that the data they provide will be collected and used in this project for design capture.

\subsubsection{Will the participants be using any non-standard hardware?}
No, hardware includes a whiteboard and pen.

\subsubsection{Is there any intentional deception of the participants?}
No intential deception of the participants is planned.

\subsubsection{How will participants voluntarily give consent?}
Reponses by participants will be anonymous, and they will give verbal consent at the time of the study.

\subsubsection{Will the participants be exposed to any risks greater than those encountered in their normal work life?}
There is no greater risk exposed to participants in this study.

\subsubsection{Are you offering any incentive to the participants?}
There is no incentive given to the participants.

\subsubsection{Are any of your participants under the age of 16?}
All participants are over the age of 16.

\subsubsection{Do any of your participants have an impairment that will limit their understanding or communication?}
None of the participants have impairments.

\subsubsection{Are you in a position of authority or influence over any of your participants?}
I am not in a position of authority over the participants.

\subsubsection{Will the participants be informed that they could withdraw at anytime?}
Of course, the participants will be informed that they can withdraw at anytime.

\subsubsection{Will the participants be informed of your contact details?}
All participants will be able to contact me after the investigation, with the details provided to them after the study.

\subsubsection{Will participants be de-briefed?}
Students will be debriefed after the study to enable them to understand the nature of the investigation.

\subsubsection{Will the data collected from the participants be stored in an anonymous form?}
All data collected will be stored on a whiteboard, with no personal information attached, ensuring anonymity.